Whittaker Models for Real Groups

### 2024-06-26 whittaker.tex
added direct argument for Wh(pi), and removed a duplicate in Refs.bib

Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in two ways.
First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}:
$$
\Wh(\pi_{\lambda_{ik}})=\WF(\pi_{\lambda_{ik}})=G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
\end{pmatrix}.
$$

>>>>

Finally let's compute $\Wh(\pi_{\lambda_{ik}})$ in three ways.

We can directly compute it as follows. Consider the  holomorphic discrete series $\pi_{in}$ with $n\ge 1$.
This has a basis 
 $\{v_j\}$ where $j=(n+1)+2i$ $(i\ge 0)$. 
The complex Lie algebra acts on this basis by
$$
\begin{aligned}
  H_\theta v_j&=jv_j\\
  E_\theta v_j&= \frac 12(n+(j+1))v_{j+2}\\
  F_\theta v_j&= \frac 12(n-(j-1))v_{j-2}\\
\end{aligned}
$$
Change basis: let $w_i=v_{n+1}+2i$ $(0\le i)$. Then
$$
\begin{aligned}
    H_\theta w_i&=(n+1+2i)w_i\\
  E_\theta w_i&=(n+1+i)w_{i+1}\\
  F_\theta w_i&= -iw_{i-1}
\end{aligned}
$$
Let's try to find a $\lambda$-eigenvector for $F_\theta$.
Solve
$$
F_\theta(\sum_{i=0}^\infty a_iw_i=\lambda\sum_{i=0}^\infty a_iw_i
$$
A short calculation gives
$$
a_{i+1}=-\frac{\lambda}{i+1}
$$
and this says that
$$
v=\sum_{i=0}^\infty \frac{\lambda^k}{(k+1)!}w_k
$$
is a $\lambda$-eigenvector.
This is not an element of the $(\g,K)$-module, but lives in its completion.
For details see [Howe-Tan].

On the other hand an $E_\theta$-eigenvector would be something like (I'm not sure the calculation is correct in all details)
$$
v=\sum_{i=0}^\infty \frac{n^{\bar i}}{\lambda^i} w_i
$$
where $n^{\bar i}=(n+1)(n+2)\dots (n+i)$.
This doesn't converge to give an element of any completion of $\pi$.

First of all by Lemma \ref{lem:matumoto}, which comes directly from \cite[Theorem A]{matumoto}:

$$
\Wh(\pi_{\lambda_{ik}})=\WF(\pi_{\lambda_{ik}})=G(\R)\cdot \begin{pmatrix}0&-\sgn(k)i\\0&0
\end{pmatrix}.
$$
